---
output: rmarkdown::github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "inst/extdata/"
)
```

## `SupMZ`: Detecting Structural Change with Heteroskedasticity 

```{r,echo = FALSE, message = FALSE}
devtools::load_all(".")
```

###### Version : [`r getNamespaceVersion("SupMZ")`](https://myaseen208.github.io/SupMZ/); Copyright (C) 2019-2020: [UAF](http://uaf.edu.pk//); License: [GPL-2|GPL-3](https://www.r-project.org/Licenses/)


##### *Muhammad Yaseen^1^, Sami Ullah^1^^,^ ^2^,  and Gulfam Haider^3^*

1. Department of Mathematics and Statistics, University of Agriculture Faisalabad, Pakistan.
2. College of Agriculutre, University of Sargodha, Pakistan.
3. Fast School of Management, FAST National University of Computer and Emerging Sciences, Chiniot Faisalabad Campus, Pakistan.

***

[![minimal R version](https://img.shields.io/badge/R>%3D-3.5.0-6666ff.svg)](https://cran.r-project.org/)
[![License: GPL v3](https://img.shields.io/badge/License-GPL%20v3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version-last-release/SupMZ)](https://cran.r-project.org/package=SupMZ)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/SupMZ?color=green)](https://CRAN.R-project.org/package=SupMZ)
<!-- [![packageversion](https://img.shields.io/badge/Package%20version-0.2.3.3-orange.svg)](https://github.com/myaseen208/SupMZ) -->

```{r, results='asis', echo=FALSE}
dver <- ifelse(test = gsub("(.\\.)(\\d+)(\\..)", "", getNamespaceVersion("SupMZ")) != "",
               yes = getNamespaceVersion("SupMZ"),
               no = gsub("Version:\\s*", "", readLines(paste0("https://raw.githubusercontent.com/", "myaseen208/SupMZ", "/master/DESCRIPTION"))[grep("Version:", readLines(paste0("https://raw.githubusercontent.com/", "myaseen208/SupMZ", "/master/DESCRIPTION")))]))
cat(paste("[![develVersion](https://img.shields.io/badge/devel%20version-", dver, "-orange.svg)](https://github.com/myaseen208/SupMZ)", sep = ""))
```

<!-- [![GitHub Download Count](https://github-basic-badges.herokuapp.com/downloads/myaseen208/SupMZ/total.svg)] -->
[![Project Status: WIP](http://www.repostatus.org/badges/latest/inactive.svg)](http://www.repostatus.org/#inactive)
[![lifecycle](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](https://github.com/myaseen208/SupMZ)
[![Rdoc](http://www.rdocumentation.org/badges/version/SupMZ)](http://www.rdocumentation.org/packages/SupMZ)
[![Analytics](https://pro-pulsar-193905.appspot.com/UA-116716530-1/welcome-page)](https://github.com/myaseen208/google-analytics-beacon)

***

## Description
`r gsub("(<doi:)(.+)(>)", "[doi:\\2](https://doi.org/\\2)", gsub("\\n", " ", packageDescription("SupMZ", fields = "Description")))`

## Installation
The package can be installed from CRAN as follows:

```{r, eval=FALSE}
install.packages("SupMZ", dependencies = TRUE)
```



The development version can be installed from github as follows:

```{r, eval=FALSE}
if (!require("remotes")) install.packages("remotes")
devtools::install_github("myaseen208/SupMZ")
```

## Detailed tutorial
For a detailed tutorial (vignette) on how to used this package type:

```{r, eval=FALSE}
browseVignettes(package = "SupMZ")
```

The vignette for the latest version is also available [online](https://myaseen208.github.io/SupMZ/articles/IntroSupMZ.html).


## What's new
To know whats new in this version type:

```{r, eval=FALSE}
news(package = "SupMZ")
```

## Links

[CRAN page](https://cran.r-project.org/package=SupMZ)

[Github page](https://github.com/myaseen208/SupMZ)

[Documentation website](https://myaseen208.github.io/SupMZ/)



## Citing `SupMZ`
To cite the methods in the package use:

```{r, eval = FALSE}
citation("SupMZ")
```

```{r, echo = FALSE}
detach("package:SupMZ", unload=TRUE)
suppressPackageStartupMessages(library(SupMZ))
cit <- citation("SupMZ")
# yr <- format(Sys.Date(), "%Y")
# cit[1]$year <- yr
# oc <- class(cit)
# 
# cit <- unclass(cit)
# attr(cit[[1]],"textVersion") <- gsub("\\(\\)",
#                                      paste("\\(", yr, "\\)", sep = ""),
#                                      attr(cit[[1]],"textVersion"))
# class(cit) <- oc
cit
